Kindly Bent to Free Us

### 2019-11-14 kindly/lang.tex
WIP pattern matching

\subsubsection{Environments and bindings}
\label{sdtyping:envs}
\begin{figure*}[tp]
  \begin{minipage}{0.28\linewidth}
    \begin{align*}
      \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
      B &::=\ \bnone \tag{Empty} \\
         &\mid \bvar{x}{\schm}\tag{Variables}\\
         &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
         &\mid \svar{x}{\schm}^n \tag{Suspended}\\
         &\mid \bvar{\tvar}{\kschm}\tag{Types}
         % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDVar
    \end{mathpar}
    \caption{The {\sc Borrow}, {\sc Abs} and {\sc Var} rules}
    \label{selectrules:borrow}
    \label{selectrules:binders}
  \end{minipage}
\end{figure*}

@@

\subsubsection{Copying and Splitting}
\label{sdtyping:split}
\begin{figure*}[tp]
  \centering
  \begin{minipage}{0.49\linewidth}
    \begin{mathpar}
      \ruleSDPair

      \ruleSDRegion
    \end{mathpar}
    % \caption{The {\sc Pair} rule}
    \caption{Selected typing rules}
    \label{sdtyp:pair}
    \label{selectrules:region}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\vdash_e$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}

@@

    \end{tabular}
    \caption{Splitting rules for bindings}
    \label{sdtyp:split}
  \end{minipage}
\end{figure*}

@@

As it would be cumbersome to markup regions manually, we developed an
algorithm that starts from each borrow, creates a region around it,
and extends it as much as possible while respecting other borrows
and binders. The algorithm (see \cref{regionannot}) also provides the region's level
and variable annotation.
Henceforth, we consider terms with fully annotated regions.

@@

% \subsubsection{Pattern matching}

>>>>

\subsubsection{Environments and bindings}
\label{sdtyping:envs}
\begin{figure*}[tp]
  \begin{minipage}{0.28\linewidth}
    \begin{align*}
      \E &::=\ \Eempty \mid \E;B\tag{Environments}\\
      B &::=\ \bnone \tag{Empty} \\
         &\mid \bvar{x}{\schm}\tag{Variables}\\
         &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
         &\mid \svar{x}{\schm}^n \tag{Suspended}\\
         &\mid \bvar{\tvar}{\kschm}\tag{Types}
         % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.7\linewidth}
    \begin{mathpar}
      \ruleSDBorrow
      \and
      \ruleSDLam
      \and
      \ruleSDVar
      \and
      \ruleSDPair
      \and
      \ruleSDRegion
      \and
      \ruleSDMatchPair
    \end{mathpar}
    \caption{Selected typing rules}
    \label{selectrules:borrow}
    \label{selectrules:binders}
    \label{sdtyp:pair}
    \label{selectrules:region}
  \end{minipage}
\end{figure*}

@@

\subsubsection{Copying and Splitting}
\label{sdtyping:split}
\begin{figure}[tp]
  % \begin{minipage}{0.5\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\vdash_e$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}

@@

    \end{tabular}
    \caption{Splitting rules for bindings}
    \label{sdtyp:split}
  % \end{minipage}
\end{figure}

@@

% As it would be cumbersome to markup regions manually, we developed an
% algorithm that starts from each borrow, creates a region around it,
% and extends it as much as possible while respecting other borrows
% and binders. The algorithm (see \cref{regionannot}) also provides the region's level
% and variable annotation.
% Henceforth, we consider terms with fully annotated regions.

@@

\subsubsection{Pattern matching}

\TODO{Present this if we have enough space}
